Mamba vs SOTA for Vision Tasks\\ \thanks{$\dagger$ Equal contributions}

### 2024-04-30 paper/main.tex
edits

\section{Input Data}\label{sec2}
We shall be using a Brain MRI segmentation dataset found in \cite{dataset}. This dataset has been used in several papers regarding classification of the shape and severity of tumors, and provides an adequate dataset for research purposes in the field of medical image analysis, particularly in the area of brain MRI segmentation. Researchers have utilized this dataset in various studies focusing on the classification of tumor shapes and the assessment of tumor severity. With its comprehensive collection of brain MRI scans, along with corresponding segmentation masks, the dataset offers valuable resources for developing and evaluating algorithms aimed at automating tumor detection and analysis.

\section{Output Data}\label{sec3}
The output of this model shall be segmentation masks for new, never before seen images.
\begin{figure}[!t]
    \centering
    \includegraphics[width=\columnwidth]{imgs/data_stats.png}
    \caption{Distributions of tumor and non-tumor images in the train, validation, and test datasets.}
    \label{fig:datastats}
\end{figure}

\section{Compared Models}
Prior to an analysis of how the Pyramidal U-Mamba compares, we shall explain what models we chose for comparison and why.

@@

@@

\section{Results for Classification Task}
To further demonstrate the viability and versatility of the Mamba architecture, we conducted experiments on the CIFAR-10 dataset \cite{krizhevsky2009learning}, a widely-used benchmark for image classification tasks. CIFAR-10 consists of 60,000 32x32 color images across 10 classes, with 6,000 images per class. The dataset is split into 50,000 training images and 10,000 test images.
For this experiment, we employed the Vision Mamba (ViM) architecture proposed by Zhu et al. \cite{zhu2024vision}. ViM is an efficient visual representation learning framework that leverages a bidirectional state space model to capture long-range dependencies in visual data. By combining the strengths of CNNs and SSMs, ViM aims to achieve competitive performance while maintaining computational efficiency.

\begin{figure}[!t]
    \centering
    \includegraphics[width=\columnwidth]{imgs/cifar_10.jpg}
    \caption{Example images from CIFAR100.}
    \label{fig:cifar}
\end{figure}

@@

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=\columnwidth]{imgs/f1_comparison.png}
    \caption{F1 scores for ViM and ViT over 100 epochs.}
    \label{fig:ViMViTF1}
\end{figure}
\begin{figure}[!t]
    \centering
    \includegraphics[width=\columnwidth]{imgs/loss_comparison.png}
    \caption{Loss scores for ViM and ViT over 100 epochs.}
    \label{fig:ViMViTLoss}
\end{figure}
\begin{figure}[!t]
    \centering
    \includegraphics[width=\columnwidth]{imgs/time_comparison.png}
    \caption{Training and validation time for ViT and ViM.}
    \label{fig:ViMViTTrainingValidationTime}
\end{figure}

>>>>

\section{Related Works}
Prior to an analysis of how the Pyramidal U-Mamba compares, we shall explain what models we chose for comparison and why.

@@

\subsection{Input Data}\label{sec2}
We shall be using a Brain MRI segmentation dataset found in \cite{dataset}. This dataset has been used in several papers regarding classification of the shape and severity of tumors, and provides an adequate dataset for research purposes in the field of medical image analysis, particularly in the area of brain MRI segmentation. Researchers have utilized this dataset in various studies focusing on the classification of tumor shapes and the assessment of tumor severity. With its comprehensive collection of brain MRI scans, along with corresponding segmentation masks, the dataset offers valuable resources for developing and evaluating algorithms aimed at automating tumor detection and analysis.

\subsection{Output Data}\label{sec3}
The output of this model shall be segmentation masks for new, never before seen images.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.75\columnwidth]{imgs/data_stats.png}
    \caption{Distributions of tumor and non-tumor images in the train, validation, and test datasets.}
    \label{fig:datastats}
\end{figure}

@@

\section{Application: Image Classification}
Here we investigate Mamba-based architectures with regards to the task of image segmentation.

\subsection{Input Data}\label{sec2}
To further demonstrate the viability and versatility of the Mamba architecture, we conducted experiments on the CIFAR-10 dataset \cite{krizhevsky2009learning}, a widely-used benchmark for image classification tasks. CIFAR-10 consists of 60,000 32x32 color images across 10 classes, with 6,000 images per class. The dataset is split into 50,000 training images and 10,000 test images.

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.75\columnwidth]{imgs/cifar_10.jpg}
    \caption{Example images from CIFAR10.}
    \label{fig:cifar}
\end{figure}

\subsection{Output Data}\label{sec3}
The output of this model will be a classification for one of the 10 classes in CIFAR10.

\section{Image Classification Models}

For this experiment, we employed the Vision Mamba (ViM) architecture proposed by Zhu et al. \cite{zhu2024vision}. ViM is an efficient visual representation learning framework that leverages a bidirectional state space model to capture long-range dependencies in visual data. By combining the strengths of CNNs and SSMs, ViM aims to achieve competitive performance while maintaining computational efficiency.

@@

\section{Results for Classification Task}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.75\columnwidth]{imgs/f1_comparison.png}
    \caption{F1 scores for ViM and ViT over 100 epochs.}
    \label{fig:ViMViTF1}
\end{figure}
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.75\columnwidth]{imgs/loss_comparison.png}
    \caption{Loss scores for ViM and ViT over 100 epochs.}
    \label{fig:ViMViTLoss}
\end{figure}
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.75\columnwidth]{imgs/time_comparison.png}
    \caption{Training and validation time for ViT and ViM.}
    \label{fig:ViMViTTrainingValidationTime}
\end{figure}
